[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-06 README/getting_started_guide.tex
Disabled LaTex for rendering plot labels

Load and run the Docker image as follows:
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
$ docker run -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}

In the initial working directory, we have a file \texttt{append.ml} that stores
the \texttt{append} function written in OCaml.
%
Given two inputs lists, the \texttt{append} function appends the first input to
the second one.
%
For each element in the first input that the function processes, it incurs a
cost ranging from 0.5 to 1.0.
%
Therefore, the worst-case cost bound of the function is $1.0 \cdot M$, where $M$
is the length of the first input list.

Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}, and
its location has already been added to the \texttt{PATH} variable so that we can
call Hybrid RaML by running \texttt{main} anywhere in the filesystem.
%
Hybrid AARA (and its artifact Hybrid RaML) provides three types of hybrid
resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.

@@

To perform Hybrid \Opt{} on the \texttt{append} function, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_opt.json
\end{verbatim}
%
In the command, \texttt{stat\_analyze} means we want to perform Hybrid AARA
(instead of the conventional AARA).
%
The input \texttt{ticks} means the resource metric of our interest is the tick
metric (instead of heap memory, for example).
%
The number 1 means we want to infer degree-1 polynomial cost bounds.
%
The input \texttt{append.ml} specifies the input file name, and the input
\texttt{append} means we want to know a cost bound of the function
\texttt{append} (instead of other functions in the same file).
%
Finally, the input \texttt{config\_opt.json} specifies the configuration file
for Hybrid \Opt{}.

@@

Simplified bound:
    0.85*M
  where
    M is the number of ::-nodes of the 1st component of the argument
\end{verbatim}
%
It means that the cost bound inferred by Hybrid \Opt{} is $0.85 \cdot M$, where
$M$ is the first input's length.

@@

Next, to perform Hybrid \BayesWC{}, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_bayeswc.json
\end{verbatim}
where the configuration file is now \texttt{config\_bayeswc.json}, which
contains hyperparameters for Bayesian inference.
%
The analysis should finish in between 40 and 50 seconds.
%
Its output on the stdout should contain
\begin{verbatim}
== append :

@@

To perform Hybrid \BayesPC{}, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_bayespc.json
\end{verbatim}
using the configuration file \texttt{config\_bayespc.json}.
%
The analysis should terminate within 90 seconds.
%
The output printed on the stdout should contain
\begin{verbatim}
== append :

@@

  Simplified bound:
     0.164309 + 0.281939*L + 2.03295*M
   where
     L is the number of ::-nodes of the 2nd component of the argument
     M is the number of ::-nodes of the 1st component of the argument
\end{verbatim}
where \texttt{0.164309 + 0.281939*L + 2.03295*M} contains the average
coefficients.

>>>>

Load and run the Docker image as follows:
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
$ docker run -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}
The current working directory is
\texttt{/home/hybrid\_aara/benchmark\_suite/playground}.

In this directory, we have a file \texttt{append.ml} that stores an OCaml
function \texttt{append}.
%
Given two inputs lists, the \texttt{append} function appends the first input to
the second one.
%
For each element in the first input that the function processes, it incurs a
cost ranging from 0.5 to 1.0.
%
Therefore, the worst-case cost bound of the function is $1.0 \cdot M$, where $M$
is the length of the first input list.

Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}.
%
Its location has already been added to the \texttt{PATH} variable so that we can
call Hybrid RaML by running \texttt{main} anywhere in the filesystem.
%
Hybrid AARA (and its implementation Hybrid RaML) provides three types of hybrid
resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.

@@

To perform Hybrid \Opt{} on the \texttt{append} function, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_opt.json
\end{verbatim}
%
In the command line, \texttt{stat\_analyze} means we perform Hybrid AARA
(instead of the conventional AARA).
%
The argument \texttt{ticks} means the resource metric of our interest is the
tick metric (instead of heap memory, for example).
%
The argument 1 means we want to infer degree-1 polynomial cost bounds.
%
The argument \texttt{append.ml} specifies the input file name, and the argument
\texttt{append} specifies the function whose cost bound we want to infer.
%
Finally, the argument \texttt{config\_opt.json} is the configuration file for
Hybrid \Opt{}.

@@

Simplified bound:
    0.85*M
  where
    M is the number of ::-nodes of the 1st component of the argument
\end{verbatim}
%
It means that the cost bound of the function \texttt{append} inferred by Hybrid
\Opt{} is $0.85 \cdot M$, where $M$ is the first input's length.

@@

Next, to perform Hybrid \BayesWC{}, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_bayeswc.json
\end{verbatim}
where the configuration file is now \texttt{config\_bayeswc.json}, which
contains hyperparameters for Bayesian inference.
%
The analysis should finish in between 40 and 50 seconds.
%
Its output on the stdout should be close to
\begin{verbatim}
== append :

@@

To perform Hybrid \BayesPC{}, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_bayespc.json
\end{verbatim}
using the configuration file \texttt{config\_bayespc.json}.
%
The analysis should terminate within 90 seconds.
%
The output printed on the stdout should be close to
\begin{verbatim}
== append :

@@

  Simplified bound:
     0.164309 + 0.281939*L + 2.03295*M
   where
     L is the number of ::-nodes of the 2nd component of the argument
     M is the number of ::-nodes of the 1st component of the argument
\end{verbatim}
where each coefficient in the inference result \texttt{0.164309 + 0.281939*L +
  2.03295*M} is the average coefficient.

### 2024-03-06 README/step_by_step_instructions.tex
Disabled LaTex for rendering plot labels

>>>>

\subsection{Benchmark Suite}

The artifact contains 10 benchmark programs for Hybrid AARA.
%
As listed in Section 7 of the paper, these benchmarks are: \texttt{MapAppend},
\texttt{Concat}, \texttt{InsertionSort2}, \texttt{QuickSort},
\texttt{QuickSelect}, \texttt{MedianOfMedians}, \texttt{ZAlgorithm},
\texttt{BubbleSort}, \texttt{Round}, and \texttt{EvenOddTail}.
%
Inside the artifact, these benchmarks are referred to as \texttt{append},
\texttt{concat}, \texttt{insertion\_sort}, \texttt{quicksort},
\texttt{quickselect}, \texttt{linear\_select}, \texttt{z\_algorithm},
\texttt{bubble\_sort}, \texttt{round}, and \texttt{even\_split\_odd\_tail}.
%
We have tested both data-driven resource analysis and hybrid resource analysis
on the first seven benchmarks, and only data-driven resource analysis on the
remaining three benchmarks.

Inside the benchmark directory \texttt{/home/hybrid\_aara/benchmark\_suite},
each benchmark has its own directory.
%
Furthermore, inside the benchmarks' directories, we have the following
directories:
\begin{enumerate}
  \item \texttt{utility}: Python source files that contain (i)
        benchmark-specific configurations for hybrid resource analysis and (ii)
        functions for analyzing the inference result.
  \item \texttt{bin}: input and output files for Hybrid RaML.
  \item \texttt{images}: plots of inferred cost bounds.
\end{enumerate}

For each benchmark, the directory \texttt{bin} already contains the experiment
results that we reported in the paper.
%
We will demonstrate how to generate the experiment results from scratch in
\cref{sec:generate experiment results}.

\subsection{Display Experiment Results}

We demonstrate how to create tables and plots in the paper from the experiment
results that are stored in each benchmark's \texttt{bin} directories.

\paragraph{Table~1}

In Table~1 in the paper, the 4\textsuperscript{th} and 5\textsuperscript{th}
columns display the proportions of sound cost bounds inferred by data-driven and
hybrid resource analyses, respectively.
%
To display these two columns, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 run_analysis.py soundness
\end{verbatim}

The 6\textsuperscript{th} and 7\textsuperscript{th} columns of Table~1 display
the analysis time of data-driven hybrid resource analyses, respectively.
To display these two columns, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 run_analysis.py time
\end{verbatim}

\paragraph{Figure~5}

Figure~5 in the paper displays relative errors of 5 selected benchmarks.
%
To create this plot, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 visualization_relative_errors.py
\end{verbatim}
%
This command creates a plot and stores it as a file
\texttt{relative\_errors.pdf} inside the directory
\texttt{/home/hybrid\_aara/benchmark\_suite/images}.
%
To view the plot, we first transfer the plot from the Docker container to the
local filesystem.
%
Run the following command in the terminal of your local machine:
\begin{verbatim}
$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite/images/relative_errors.pdf 
    <path_to_local_directory>
\end{verbatim}
where the second argument \texttt{<path\_to\_local\_directory>} is the
destination directory on your local filesystem.
%
You can then view it on your local machine.

\subsection{Generate Experiment Results}
\label{sec:generate experiment results}
